EoS-insensitive relations after GW170817

### 2019-02-09 paper/bin-love-after-gw170817.tex
Switched some figures to absolute differences

\begin{table}
\centering
\caption{
Comparison between the EoS-insensitive relations (I-Love-Q, C-Love, R-Love, and binary Love) maximal EoS variability for the results of previous works~\cite{Yagi:ILQ,Yagi:binLove}, and the unconstrained and constrained sets of EoSs analyzed here. 
The maximum EoS variation, given by the largest fractional difference (the R-Love variability is shown as the absolute difference in m here) from the fits as shown in Figs.~\ref{fig:ILQ},~\ref{fig:clove},~\ref{fig:rlove} and~\ref{fig:binLove}, observes a considerable improvement for the constrained set of EoSs, compared to the unconstrained set as well as that found in previous works.
Additionally, note how the maximal EoS variation for the unconstrained set of EoSs is slightly larger than that found in Refs.~\cite{Yagi:ILQ,Yagi:binLove} - due to the effects of large random sampling taking into account more sources of uncertainty.
}\label{tab:maxVar}
\begin{tabular}{ c  || c c c } 
 \hline
 \hline
 \textbf{EoS-insensitive} & \multicolumn{3}{c}{\textbf{Maximal EoS Variability}} \\
 \cline{2-4}
 \textbf{Relation} & \multicolumn{1}{c|}{\emph{Previous}} & \multicolumn{1}{c|}{\emph{Unconstrained}} & \emph{Constrained}\\
 \hline
 $\bar{I}-\Lambda$ &  $0.0059$ & $0.007673$ & $0.003138$\\
 $\bar{Q}-\Lambda$ & $0.010$ & $0.01262$ & $0.004661$\\
 $\bar{I}-\bar{Q}$ & $0.012$ & $0.01490$ & $0.005716$\\
 \hline
 $C-\Lambda$ & $0.065$ & $0.07198$ & $0.02169$\\
 $R-\Lambda$ & -- & $358.9 \text{ m}$ & $881.4 \text{ m}$\\
 \hline
 $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.50$} & \multirow{2}{*}{$0.5724$} & \multirow{2}{*}{$0.2140$}\\
 $(q=0.90)$ & & &\\
 \cline{1-1}
 $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.20$} & \multirow{2}{*}{$0.2447$} & \multirow{2}{*}{$0.08284$}\\
  $(q=0.7)$ & & &\\
  \cline{1-1}
 $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.025$} & \multirow{2}{*}{$0.03841$} & \multirow{2}{*}{$0.01823$}\\
  $(q=0.50)$ & & &\\
  \cline{1-1}
\hline
\hline
\end{tabular}
\end{table}

@@

Figure~\ref{fig:clove} presents the C-Love relations for both the constrained and unconstrained sets of EoSs, along with the relative fractional difference from the fits. 
Observe how the constrained EoSs show a large suppression in EoS variability compared to the unconstrained EoSs, as well as to that found in previous works~\cite{Yagi:binLove}.
The maximal EoS variation is compared between the above three cases in Tab.~\ref{tab:maxVar}.
\begin{figure}
\begin{center} 
\includegraphics[width=.86\columnwidth]{CL.eps}
\end{center}
\caption{
Similar to Fig.~\ref{fig:ILQ} but for C-Love relations.
In this figure, we similarly construct fits to  Eq.~\ref{eq:ILQfitNew}, properly limiting to the Newtonian case $C \sim \Lambda^{-1/5}$.
Observe how, as before, the fractional difference from the fits is greatly suppressed for the constrained case, compared to both the unconstrained case, and results from previous works~\cite{Yagi:binLove}.
The maximal EoS variation from the fits for the unconstrained and constrained sets of EoSs are compared in Tab.~\ref{tab:maxVar}.
Additionally shown in this figure is the hybrid star C-Love relations along with their fractional difference from the constrained EoS fits (dashed green).
}
\label{fig:clove}
\end{figure}

@@

\begin{figure}
\begin{center} 
\includegraphics[width=1\columnwidth]{RL.eps}
\end{center}
\caption{
Similar to Fig.~\ref{fig:clove} but for the R-Love relationship between the NS radius and tidal deformability.
This relationship is computed directly from the C-Love relations, and estimates the uncertainty on the NS radius as computed through the C-Love relations.
Observe how the absolute difference from the fit is reduced significantly between the unconstrained and constrained sets of EoSs, shown by the comparisons in Tab.~\ref{tab:maxVar}.
}
\label{fig:rlove}
\end{figure}

>>>>

\begin{table}
\centering
\caption{
Comparison between the EoS-insensitive relations (I-Love-Q, C-Love, R-Love, and binary Love) maximal EoS variability for the results of previous works~\cite{Yagi:ILQ,Yagi:binLove}, and the unconstrained and constrained sets of EoSs analyzed here. 
The maximum EoS variation, given by the largest fractional difference (the absolute difference is also shown in parenthesis for the C-Love, R-Love, and binary Love fits) from the fits as shown in Figs.~\ref{fig:ILQ},~\ref{fig:clove},~\ref{fig:rlove} and~\ref{fig:binLove}, observes a considerable improvement for the constrained set of EoSs, compared to the unconstrained set as well as that found in previous works.
Additionally, note how the maximal EoS variation for the unconstrained set of EoSs is slightly larger than that found in Refs.~\cite{Yagi:ILQ,Yagi:binLove} - due to the effects of large random sampling taking into account more sources of uncertainty.
}\label{tab:maxVar}
\begin{tabular}{ c  || c c c } 
 \hline
 \hline
 \textbf{EoS-insensitive} & \multicolumn{3}{c}{\textbf{Maximal EoS Variability}} \\
 \cline{2-4}
 \textbf{Relation} & \multicolumn{1}{c|}{\emph{Previous}} & \multicolumn{1}{c|}{\emph{Unconstrained}} & \emph{Constrained}\\
 \hline
 $\bar{I}-\Lambda$ &  $0.0059$ & $0.007673$ & $0.003138$\\
 $\bar{Q}-\Lambda$ & $0.010$ & $0.01262$ & $0.004661$\\
 $\bar{I}-\bar{Q}$ & $0.012$ & $0.01490$ & $0.005716$\\
 \hline
 \noalign{\smallskip}
\noalign{\smallskip}
 \noalign{\smallskip}
\noalign{\smallskip}
\hline
 \hline
 \textbf{EoS-insensitive} & \multicolumn{3}{c}{\textbf{Maximal EoS Variability}} \\
 \cline{2-4}
 \textbf{Relation} & \multicolumn{1}{c|}{\emph{Previous}} & \multicolumn{1}{c|}{\emph{Unconstrained}} & \emph{Constrained}\\
 \hline
 \multirow{2}{*}{$C-\Lambda$} & $0.065$ & $0.07198$ & $0.02169$\\
 & (--) & ($0.01837$) & ($0.006582$)\\
  \hline
 \multirow{2}{*}{$R-\Lambda$} & -- & $0.02172$ & $0.05649$\\
 & (--) & ($358.9 \text{ m}$) & ($881.4 \text{ m}$)\\
 \hline
 $\Lambda_a-\Lambda_s$ & $\sim0.50$ & $0.5724$ & $0.2140$\\
 $q=0.90$ & (--) & ($190.1$) & ($37.23$) \\
 \cline{1-1}
 $\Lambda_a-\Lambda_s$ & $\sim0.20$ & $0.2447$ & $0.08284$\\
  $q=0.7$ & (--) & ($320.4$) & ($51.62$) \\
  \cline{1-1}
 $\Lambda_a-\Lambda_s$ & $\sim0.025$ & $0.03841$ & $0.01823$\\
  $q=0.50$ & (--) & ($244.1$) & ($28.96$) \\
  \cline{1-1}
\hline
\hline
\end{tabular}
\end{table}

@@

Figure~\ref{fig:clove} presents the C-Love relations for both the constrained and unconstrained sets of EoSs, along with the relative fractional difference from the fits. 
Observe how the constrained EoSs show a large suppression in EoS variability compared to the unconstrained EoSs, as well as to that found in previous works~\cite{Yagi:binLove}.
The maximal EoS variation is compared between the above three cases in Tab.~\ref{tab:maxVar}.
\begin{figure}
\begin{center} 
\includegraphics[width=\columnwidth]{CL.eps}
\end{center}
\caption{
Similar to Fig.~\ref{fig:ILQ} but for C-Love relations.
In this figure, we similarly construct fits to  Eq.~\ref{eq:ILQfitNew}, properly limiting to the Newtonian case $C \sim \Lambda^{-1/5}$.
Observe how, as before, the fractional difference from the fits is greatly suppressed for the constrained case, compared to both the unconstrained case, and results from previous works~\cite{Yagi:binLove}.
The maximal EoS variation from the fits for the unconstrained and constrained sets of EoSs are compared in Tab.~\ref{tab:maxVar}.
Additionally shown in this figure is the hybrid star C-Love relations along with their fractional difference from the constrained EoS fits (dashed green).
}
\label{fig:clove}
\end{figure}

@@

\begin{figure}
\begin{center} 
\includegraphics[width=\columnwidth]{RL.eps}
\end{center}
\caption{
Similar to Fig.~\ref{fig:clove} but for the R-Love relationship between the NS radius and tidal deformability.
This relationship is computed directly from the C-Love relations, and estimates the uncertainty on the NS radius as computed through the C-Love relations.
Observe how the absolute difference from the fit is reduced significantly between the unconstrained and constrained sets of EoSs, shown by the comparisons in Tab.~\ref{tab:maxVar}.
}
\label{fig:rlove}
\end{figure}
